What is disputed on the web?

### 2010-02-02 papers/wicow_claimfinder/claimfinder.tex
Folded in John Mark's changes

\author{
\alignauthor Rob Ennals\\
       \affaddr{Intel Labs Berkeley}\\
       \affaddr{2150 Shattuck Ave}\\
       \affaddr{Berkeley, CA, USA}\\
       \email{robert.ennals@intel.com}
\alignauthor Dan Byler\\
       \affaddr{School of Information}\\
       \affaddr{University of California at Berkeley}\\
       \affaddr{Berkeley, CA, USA}\\
       \email{daniel.byler@berkeley.edu}
\and
\alignauthor John Mark Agosta\\
       \affaddr{Intel Labs Santa Clara}\\
       \affaddr{2200 Mission College Blvd}\\
       \affaddr{Santa Clara, CA, USA}\\
       \email{john.m.agosta@intel.com}
\alignauthor Barbara Rosario\\
       \affaddr{Intel Labs Santa Clara}\\
       \affaddr{2200 Mission College Blvd}\\
       \affaddr{Santa Clara, CA, USA}\\
       \email{john.m.agosta@intel.com}
}

@@

\resolved{too much emphasis on {\em how}... rewrite following paragraph}

@@

The web contains a vast number of pages written by a vast number of people. In many cases, these people disagree with each other, and the pages they write contain conflicting information. For users to extract reliable information from the web, it is useful for them to be able to determine when different sources disagree about a topic.

In this paper we describe a method for automatically acquiring a corpus of disputed claims from the web. We consider a claim to be {\it disputed} if a page exists on the web that suggests both that the claim is false, and that there are others that are making the claim. We are also interested in {\it who} disputes a particular claim, since a user is likely to be more interested in being told that a claim is disputed by a large number of sources that they believe are credible, rather than a small number of sources that they do not trust.

We identify disputed claims by searching for lexical patterns such as ``the misconception that $S$'' (Section~\ref{findingclaims}). For example, if a page contains the text ``the misconception that {\it the moon is made of cheese}'', this suggests that the author believes that others are saying that the moon is made of cheese, and that the author themselves disputes this claim. In Figure~\ref{templates} we list some of the patterns we used. In practice, many of the strings that match such a pattern are not well-formed disputed claims. We use a statistical classifier to filter out those strings that appear to make a well-formed claim.

We believe that this corpus will be useful for many purposes. We are currently using it as part of our Dispute Finder~\cite{Ennals2010} project to automatically highlight phrases on web pages that are disputed by other sources. We are also exploring other applications of this corpus, including automatically detecting disputed claims in human speech, visualization tools that let users know what is disputed about a topic that interests them, and statistical tools that allow people to look for patterns in Internet debate  (Section~\ref{using}).

@@

There are several ways that a user can determine whether to trust information that they find on a web page. The user can check the reputation of the person or organization that wrote the web page; they can observe whether the web page meets their aesthetic criteria for a reliable web page; or they can check whether the information is consistent with information available from other sources.

A user can check the reputation of a source using a service such as SourceWatch.org, which publishes manually curated information about the reputation and known biases of various sources. Trustpilot.com produce a Firefox extension that warns a user when they are looking at a web page hosted by a company that they believe is not trustworthy. Alternatively, a user can simply use a search engine such as Google to look for information about the source. While these tools can be very useful, trustworthy sources sometimes publish unreliable information, and untrusted sources sometimes contain useful information. For example, a reliable source may have been misled by an unreliable source they were using themselves; or a small unrated blog may publish information that useful, insightful, and accurate.

@@

The problem of detecting disputed claims is closely related to the well-studied problem of detecting contradictions. A claim $H$ is {\it contradicted} if a document somewhere on the web makes a claim that implies that $H$ cannot be true. For example, the claim ``The moon is made of rock'' {\it contradicts} the claim ``The moon is made of cheese''. A contradicted claim is not necessarily a disputed claim. In this example the person who said that the moon was made of rock might not be aware that others think it is made of cheese. A {\it contradiction} is logical, while a {\it dispute} is social. In order for a claim to be disputed, the authors of the documents must be aware that there is a contradiction between their beliefs.

@@

Detecting contradictions has proven to be a hard problem~\cite{Giampiccolo2007}. Much of this difficulty comes from the fact that one typically needs deep semantic and contextual knowledge to determine whether two statements that look like they might contradict each other actually do. For example ``George Bush is married to Barbara Bush'' does not contradict ``George Bush is married to Laura Bush'' because there is more than one George Bush. ``Alan Turing was born in England'' does not contradict ``Alan Turing was born in London'' because London is in England. ``It is raining is San Francisco'' does not contradict ``It is not raining in San Francisco'' if the statements were made at different times.

We detect disputes rather than contradictions. Rather than looking for claims that contradict each other, we look for evidence that people believe that there is a contradiction and that this contradiction is important. One advantage of looking for disputes rather than contradictions is that this allows humans to do the hard work of identifying contradictions and deciding whether they are important. If a page says ``Falsely claimed that George Bush is married to Barbara Bush'' then that suggests that the contradiction with ``George Bush is married to Laura Bush'' is likely to be genuine. The corresponding disadvantage is that if one looks for disputes, one will only detect contradictions that humans have found and believe are important.

@@

We implemented a three-stage process to build our corpus of disputed claims, each described in the following Sections. We first create a set of lexical patterns such as ``the misconception that'' and ``it is not the case that'' (Section~\ref{patterns}). We then search the Web for these patterns (Section~\ref{searchpattern}). Finally, we filter the resulting strings to give only those that resemble unambiguous disputed claims (Section~\ref{filterclaim}).

@@

This is an instance of template inference (aka pattern matching), a method that has been used extensively for many NLP tasks. Hearst~\cite{Hearst1992} searched for templates such as ``$X$ such as $Y$'' to infer hyponyms, and Riloff~\cite{Riloff1993} searched for words such as ``kidnapped'' to find information about terrorist events. TextRunner~\cite{Etzioni2008} searches for more general patterns to extract logical relationships from the web.
These methods differ on how {\bf finish here}
\x{add more related work here}
\todo{add more related work here}

@@

Not all patterns have exactly the same meaning. We grouped our patterns into three loose group, based on manual inspection of the pages that use them (Figure~\ref{templates}):

@@

 \item {\bf Plausible to not believe it:} The author feels the need to say that someone believes it, implying that it it plausible that someone else might not believe it. This is only subtly different from the previous group. For example ``Fans believe that {\it Elvis is alive}'' is less strong than ``Fans are claiming that {\it Elvis is alive}''. It is useful to exclude the cases where the pattern is prefixed by ``I'', since such sentences rarely contain useful disputed claims. For example ``John thinks Elvis is dead'' implies much more skepticism than ``I think Elvis is dead''. 
 \end{itemize}

@@

Figure~\ref{filtered} shows some examples of the kind of strings that can match our patterns and the reasons why we might want to filter some of them out. a chunk of text might not be a factual statement (case 1), it might include unbound referents such as ``it'' or ``they'' (case 2), or it might by ambiguous what entities it is referring to (case 3).

The {\it P} column in Figure~\ref{templates} shows the percentage of the strings that match each pattern that we estimate to be unambiguous falsifiable claims. We estimated the precision of each pattern by randomly selecting 100 strings that match the pattern and then manually marking strings that we subjectively decided were well formed and unambiguous.

@@

We can observe that the patterns in the ``something false'' group perform much better than the patterns in ``plausible to not believe it'' group, but the ``plausible to not believe it'' group has a lot more hits. For the best patterns our classifier has accuracy in the high seventies.

Manual inspection suggests that the classifier is fairly good at filtering out strings that are not claims (case 1) but does poorly at working out whether a claim is unambiguous. This is not surprising. We anticipate that a more sophisticated technique with real world knowledge would be needed in order to determine whether a claim was unambiguous.

@@

A third category of applications could be broadly classified as research tools: agents which allow users to explore what is disputed about a particular topic, or to more broadly examine the zeitgeist of disputes. As an increasing proportion of human knowledge is brought to the web, these tools will be increasingly important in sociological and historical research.

@@

These graphs resemble those produced by MemeTracker~\cite{Backstrom2009}, which graphed when particular memes were discussed on the web. They tracked highly repeated phrases, rather than nouns used in disputed claims.

@@

@@

%\section{Acknowledgments}

\todo{Do we want to have acknowledgements}
% We would like to Thank Barbara Rosario for help with textual entailment, and 
% Acknowledgements omitted for blind submission. Dispute Finder uses icons from the free FamFamFam Silk\footnote{http://famfamfam.com} collection.

>>>>

\author{
\alignauthor Rob Ennals\\
       \affaddr{Intel Labs Berkeley}\\
       \affaddr{2150 Shattuck Ave}\\
       \affaddr{Berkeley, CA, USA}\\
       \email{robert.ennals@intel.com}
\alignauthor Dan Byler\\
       \affaddr{School of Information}\\
       \affaddr{University of California at Berkeley}\\
       \affaddr{Berkeley, CA, USA}\\
       \email{daniel.byler@berkeley.edu}
\and
\alignauthor John Mark Agosta\\
       \affaddr{Intel Labs Santa Clara}\\
       \affaddr{2200 Mission College Blvd}\\
       \affaddr{Santa Clara, CA, USA}\\
       \email{john.m.agosta@intel.com}
\alignauthor Barbara Rosario\\
       \affaddr{Intel Labs Santa Clara}\\
       \affaddr{2200 Mission College Blvd}\\
       \affaddr{Santa Clara, CA, USA}\\
       \email{barbara.rosario@intel.com}
}

@@

@@

The web contains a vast number of pages written by a vast number of people. In many cases, these people disagree with each other, and the pages they write contain conflicting information. For users to extract reliable information from the web, it is important that they be able to determine the credibility of the information that they read. One way to determine whether information is credible is to check whether it is disputed by other sources.

In this paper we describe a method for automatically acquiring a corpus of disputed claims from the web. We use the word {\it claim} to mean a statement of opinion or fact contained in the text of a web page. 
We consider a claim to be {\it disputed} if a page exists on the web that suggests both that the claim is false, and also that there are others that are making the claim. We are also interested in {\it who} disputes a particular claim, since a user is likely to be more interested in being told that a claim is disputed by a large number of sources that they believe are credible, rather than a small number of sources that they do not trust.

We identify disputed claims by searching for lexical patterns such as ``the misconception that'' (Section~\ref{findingclaims}). For example, if a page contains the text ``the misconception that {\it the moon is made of cheese}'', this suggests that the author believes that others are saying that the moon is made of cheese, and that the author themselves disputes this claim. In Figure~\ref{templates} we list some of the patterns we used. In practice, many of the strings that match such a pattern are not well-formed disputed claims. We use a statistical classifier to select only those strings that appear to make a well-formed claim.

We believe that this corpus or disputed claims will be useful for many purposes. We are currently using it as part of our Dispute Finder~\cite{Ennals2010} project to automatically highlight phrases on web pages that are disputed by other sources. We are also exploring other applications of this corpus, including automatically detecting disputed claims in human speech, visualization tools that let users know what is disputed about a topic that interests them, and statistical tools that allow people to look for patterns in Internet debate  (Section~\ref{using}).

@@

There are several ways that a user can determine whether to trust information that they find on a web page. The user can check the reputation of the person or organization that wrote the web page; they can observe whether the web page looks how they expect a credible source to look; or they can check whether the information is consistent with information available from other sources.

A user can check the reputation of a source using a service such as SourceWatch.org, which publishes manually curated information about the reputation and known biases of various sources. Trustpilot.com produce a Firefox extension that warns a user when they are looking at a web page hosted by a company that they believe is not trustworthy. Alternatively, a user can simply use a search engine such as Google to look for information about the source's reputation. While these tools can be very useful, trustworthy sources sometimes publish unreliable information, and untrusted sources sometimes contain useful information. For example, a reliable source may have been misled by an unreliable source they were using themselves; or a small unrated blog may publish information that is useful, insightful, and accurate.

@@

The problem of detecting disputed claims is closely related to the well-studied problem of detecting contradictions. A claim $H$ is {\it contradicted} if a document somewhere on the web makes a claim that implies that $H$ cannot be true. For example, the claim ``The moon is made of rock'' {\it contradicts} the claim ``The moon is made of cheese''. 
But a contradicted claim is not necessarily a disputed claim. In this example the person who said that the moon was made of rock might not be aware that others think it is made of cheese. A {\it contradiction} is logical, while a {\it dispute} is social. In order for a claim to be disputed, the authors of the documents must be aware that there is a contradiction between their beliefs.

@@

Detecting contradictions has proven to be a hard problem~\cite{Giampiccolo2007}. Much of this difficulty comes from the fact that one typically needs deep semantic and contextual knowledge to determine whether two statements that look like they might contradict each other actually do. 
Two instances of the same phrase may have the same sense, but a different reference, or two different phrases may refer to the same thing. 
For example ``George Bush is married to Barbara Bush'' does not contradict ``George Bush is married to Laura Bush'' because there is more than one George Bush. ``Alan Turing was born in England'' does not contradict ``Alan Turing was born in London'' because London is in England. ``It is raining is San Francisco'' does not contradict ``It is not raining in San Francisco'' if the statements were made at different times. ``The company is not going bust'' does not contract ``the company is doing great'' if the statements are about different companies.

We detect disputes rather than contradictions. Rather than looking for claims that contradict each other, we look for linguistic clues that writers believe that there is a contradiction between what they believe and what others believe; and that this contradiction is important. One advantage of looking for disputes rather than contradictions is that this allows humans to do the hard work of identifying contradictions and deciding whether they are important. If a page says ``Falsely claimed that Obama is a Muslim'' then that suggests that the contradiction with ``Obama is a Muslim'' is likely to be genuine. 
The corresponding disadvantage would be that if one looks for disputes, one would only detect contradictions that humans have found and believe are important.

@@

We implemented a three-stage process to build our corpus of disputed claims, each described in the following Sections. We first create a set of lexical patterns such as ``the misconception that'' and ``it is not the case that'' (Section~\ref{patterns}). We then search the Web for these patterns (Section~\ref{searchpattern}) to collect sentences that contain the pattern, followed by some other string. Finally, we filter the resulting strings to give only those that resemble unambiguous falsifiable claims (Section~\ref{filterclaim}).

@@

This is an instance of template inference (aka pattern matching), a method that has been used extensively for many NLP tasks. Hearst~\cite{Hearst1992} searched for templates such as ``$X$ such as $Y$'' to infer hyponyms, and Riloff~\cite{Riloff1993} searched for words such as ``kidnapped'' to find information about terrorist events. TextRunner~\cite{Etzioni2008} searches for more general patterns to extract logical relationships from the web.

@@

\input{modals}

Not all patterns have exactly the same meaning. We grouped our patterns into three loose groups, based on manual inspection of the pages that use them (Figure~\ref{templates}):

@@

 \item {\bf Plausible to not believe it:} The author feels the need to say that someone believes it, implying that it is plausible that someone else might not believe it. This is only subtly different from the previous group. For example ``Fans believe that {\it Elvis is alive}'' is less strong than ``Fans are claiming that {\it Elvis is alive}''. It is useful to exclude the cases where the pattern is prefixed by ``I'', since such sentences rarely contain useful disputed claims. For example ``Some believe that Elvis is dead'' implies much more skepticism than ``I believe Elvis is dead''. 
 \end{itemize}

@@

Figure~\ref{filtered} shows some examples of the kind of strings that can match our patterns and the reasons why we might want to filter some of them out. A chunk of text might not be a factual statement (case 1), it might include unbound referents such as ``it'' or ``they'' (case 2), or it might otherwise be ambiguous what entities it is referring to (case 3).

The {\it P} column in Figure~\ref{templates} shows the precision for different patterns. 
This is the estimated percentage of the strings that match the pattern that are unambiguous falsifiable claims. We estimated the precision of each pattern by randomly selecting 100 strings that match the pattern and then manually marking strings that we subjectively decided were well formed and unambiguous.

@@

We can observe that the patterns in the ``something false'' group have much higher precision than the ``plausible to not believe it'' group, but have a lot less hits. Similarly, we can observe that our classifier performs much better on the ``something false'' patterns, with accuracy getting into the high seventies.

Manual inspection suggests that the classifier is fairly good at filtering out strings that are not claims (case 1) but does poorly at working out whether a claim is unambiguous. This is not surprising. We anticipate that a more sophisticated technique with real world knowledge would be needed in order to accurately determine whether a claim was unambiguous.

@@

A third category of applications could be broadly classified as research tools: agents which allow users to explore what is disputed about a particular topic, or to more broadly examine the social dynamics of disputes on the web. As an increasing proportion of human knowledge is brought to the web, these tools will be increasingly important in sociological and historical research.

@@

These graphs resemble those produced by MemeTracker~\cite{Backstrom2009}, which graphed when particular memes were discussed on the web. They tracked highly repeated phrases, rather than nouns used in disputed claims. Kittur et al~\cite{Kittur2009} graphed the categories on Wikipedia that contained the most conflict.

@@

In the future, we plan to use ideas from textual entailment~\cite{Giampiccolo2007} to cluster claims together directly, and then automatically train a classifier that we can use to identify other claims on the web that are likely to have a similar meaning.

@@
